\LARGE How coexistence mechanisms mediate temporal stability

### 2014-11-03 manuscript/ms_CoexistStability.Rnw
new figure of model

\subsection{A general consumer-resource model}
We start with a general consumer-resource model where the consumer can be in one of two-states: a dormant state $D$ and a live state $N$. Transitions between $N$ and $D$ occur at discrete intervals $T$, so our model is formulated as ``pulsed differential equations". For clarity we refer to $T$ as years and the growing time between years, $\tau$, as seasons. Seasonal (within-year) dynamics are modeled as three differential equations:
\begin{align}
\frac{\text{d}D_{i}}{\text{d}\tau} &= -(m_{D,i}D_{i})\\
\frac{\text{d}N_{i}}{\text{d}\tau} &= f(R)N_{i} - m_{N,i}\\
\frac{\text{d}R_{i}}{\text{d}\tau} &= a(S - R) - \sum\limits_{i=1,2}f(R)N_{i}
\end{align}
where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $N$ is the living biomass (fast-growing, shorter-lived) state, and $m$s are biomass loss rates. The growth rate of living biomass is a resource-dependent function, $f(R) = r_{i}R/(K_{i}+R)$, where $r$ is the maximum growth rate and $K$ is the resource level at which growth is one-half $r$. For the resource dynamics, whose state is denoted by $R$, we use a linear resource renewal equation where $a$ scales resource turnover rate and $S$ is the resource equilibrium when consumers are absent, and an offtake of the resource equal to the sum of each species' consumption, $\sum_{i=1,2}f(R)N_{i}$. Note that since transitions between $N$ and $D$ are pulsed, only biomass loss occurs throughout the season for $D$.

>>>>

\subsection{A general consumer-resource model}
We start with a general consumer-resource model where the consumer can be in one of two-states: a dormant state $D$ and a live state $N$ (Figure~\ref{fig:model}). Transitions between $N$ and $D$ occur at discrete intervals $T$, so our model is formulated as ``pulsed differential equations". For clarity we refer to $T$ as years and the growing time between years, $\tau$, as seasons. Seasonal (within-year) dynamics are modeled as three differential equations:
\begin{align}
\frac{\text{d}D_{i}}{\text{d}\tau} &= -(m_{D,i}D_{i})\\
\frac{\text{d}N_{i}}{\text{d}\tau} &= f(R)N_{i} - m_{N,i}N_{i}\\
\frac{\text{d}R_{i}}{\text{d}\tau} &= a(S - R) - \sum\limits_{i=1,2}f(R)N_{i}
\end{align}
where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $N$ is the living biomass (fast-growing, shorter-lived) state, and $m$s are biomass loss rates. The growth rate of living biomass is a resource-dependent function, $f(R) = r_{i}R/(K_{i}+R)$, where $r$ is the maximum growth rate and $K$ is the resource level at which growth is one-half $r$. For the resource dynamics, whose state is denoted by $R$, we use a linear resource renewal equation where $a$ scales resource turnover rate and $S$ is the resource equilibrium when consumers are absent, and an offtake of the resource equal to the sum of each species' consumption, $\sum_{i=1,2}f(R)N_{i}$. Note that since transitions between $N$ and $D$ are pulsed, only biomass loss occurs throughout the season for $D$.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{"SemiDiscreteModel"}
\caption{Schematic of our semi-discrete consumer-resource model. See text for parameter definitions.}
 \label{fig:model}
\end{figure}
